### 2016-05-11 experiment/processing/attempts-bridge-proxy.tex
Move autogenerated tables into separate files.

\documentclass[USenglish,oneside,twocolumn]{article}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}
%\usepackage{hyperref}

\usepackage[utf8]{inputenc}%(only for the pdftex engine)
%\RequirePackage[no-math]{fontspec}%(only for the luatex or the xetex engine)
\usepackage[big]{dgruyter_NEW}

\DOI{foobar}

\cclogo{\includegraphics{by-nc-nd.pdf}}

% Format a participant quotation.
\newcommand{\pquote}[2]{
\begin{quotation}
\noindent #1:~\textit{``#2''}
\end{quotation}
}

\begin{document}

  \author*[1]{Linda Lee}

  \author[2]{David Fifield}

  \author[3]{Nathan Malkin}

  \author[4]{Ganesh Iyer}

  \author[5]{Serge Egelman}

  \author[6]{David Wagner}

  \affil[1]{University of California Berkeley, E-mail: \mbox{lnl@cs.berkeley.edu}}

  \affil[2]{University of California Berkeley, E-mail: \mbox{fifield@cs.berkeley.edu}}

  \affil[3]{University of California Berkeley, E-mail: \mbox{nmalkin@cs.berkeley.edu}}

  \affil[4]{University of California Berkeley, E-mail: \mbox{ganesh.v@berkeley.edu}}

  \affil[5]{University of California Berkeley and International Computer Science Institute, E-mail: \mbox{egelman@cs.berkeley.edu}}

  \affil[6]{University of California Berkeley, E-mail: \mbox{daw@cs.berkeley.edu}}

  \title{\huge Tor's Usability for Censorship Circumvention}
  %Internet Freedom Made Easy: On Improving Tor’s Usability for Censorship Circumvention
  %Towards Usable Censorship Circumvention

  \runningtitle{Tor's Usability for Censorship Circumvention}

  %\subtitle{...}

  \begin{abstract}
{Tor has grown beyond its original purpose as an anonymity tool and has 
become a widely-used censorship circumvention tool.
This is the first study to examine Tor's usability in this role.
We evaluate, design, and test the Tor configuration interface by
placing users in simulated censorship environments, instructing them to use Tor
to circumvent censorship, and measuring their interactions with the interface.
A 16-participant qualitative user study identifies common user struggles while circumventing censorship.
We use the results as feedback to redesign the configuration interface.
A 114-participant quantitative user study tests the impact of our changes.
We find that our changes result in a significant reduction 
in the time spent configuring a connections. We
conclude with recommendations for changes to the current interface as well as 
alternative approaches to bootstrapping a connection to Tor.}
\end{abstract}
  \keywords{User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

  \journalname{Proceedings on Privacy Enhancing Technologies}
\DOI{Editor to enter DOI}
  \startpage{1}
  \received{..}
  \revised{..}
  \accepted{..}

  \journalyear{2015}
  \journalvolume{2015}
  \journalissue{2}

\maketitle

\section{Introduction}

Tor is an anonymity network that routes traffic through a series of relays
that make it difficult to observe the source and destination~\cite{dingledine2004tor}. Tor's anonymizing functionality also circumvents censorship. Using Tor for censorship circumvention became sufficiently common that many countries attempt to block Tor for this reason~\cite{winter2012great}. Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network less obvious, and advanced techniques to resist blocking.

This is the first user study that investigates the usability of Tor as a censorship circumvention tool. Our experiments are both a case study observing users circumvent censorship and a step toward helping current Tor users by making censorship circumvention easier. All Tor users benefit from improving the configuration interface, and thereby increasing the adoption of Tor as a censorship circumvention tool. Users who successfully use Tor to circumvent censorship are provided with extra security features that other censorship circumvention tools do not provide, while users who use Tor as an anonymity system benefit from an increased number of overall users on the Tor network~\cite{dingledine2006anonymity}.

We evaluate, redesign, and test Tor's configuration interface by
measuring participants' interactions with the interface in various censorship environments.
The first user study is a small-scale, qualitative experiment that collected 
behavioral patterns and failure cases with the interface through user observations
and interviews (Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, quantitative experiment
that collected data on user interactions with the interface to quantify the impact of the design changes (Section~\ref{sec:quantitative}).

In this paper, we contribute the following:
\smallskip
\begin{itemize}
\item 6 common challenges encountered during the configuration process and their underlying causes
\item 10 changes to the configuration interface which we hope alleviates the common challenges
\item 114 logs of real world user attempts to connect to Tor in three different censorship environments
\item 4 reasons why users failed to connect to Tor
\item 5 recommendations of configuration interface changes to help more users connect and save time
\item 5 alternative  approaches to bootstrapping a connection that leverage varying degrees of automation
\end{itemize}
We hope that our work helps users circumvent censorship and connect to Tor.

\section{Related Work} 
There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and FoxyProxy, and found that none had satisfactory from a usability. Fabian et~al.~\cite{fabian2010privately} show that Tor's added
latency~\cite{dingledine2009performance} causes users
to be frustrated, cancel requests, and prevents user adoption. 
Norcie et~al.~\cite{norcie2012eliminating} found found that 
64\% of users are unable to continue with installation or browsing at least once due to difficulties.

We do not know of any published usability evaluations of
Tor Browser since the release of the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
The most recent effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
some of which influenced changes in Tor Browser version~4.5 and later.

Previous user studies have considered the whole browsing experience,
without focusing on specific features in isolation.
Our study focuses on 
the browser's configuration interface, which guides users through setting up components required to circumvent censorship.

\section{Background}
This section provides the necessary background the configuration interface relates to Tor, the network components that are involved in censorship circumvention, and the configuration settings are required to bypass levels of Tor-adverse censorship environments.

\subsection{Tor, Tor Browser, and Tor Launcher}
The recommended way to use Tor is through Tor Browser~\cite{torbrowser},
a modified Firefox browser that includes a built-in Tor client.
Tor Browser has a component called Tor Launcher that
starts, stops, and otherwise controls the underlying Tor processes.
Tor Launcher's graphical user interface gives access to 
sophisticated circumvention mechanisms, giving the user
the option to configure a proxy and bridge before connecting to Tor
for the first time. This is the object of our study.

In principle, the process of configuring a proxy and bridge can be automated, but
the interface eschews automatic configuration through network probing
in favor of guided manual configuration to give users agency in configuring their connection. 
Automatic configuration through network probing may put some users in certain regimes at risk. 
A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
However, this requires that the user grapple with technical concepts such as 
bridges, pluggable transports, and proxies. Some of these concepts are specific to 
Tor and not general concepts.

\subsection{Bridges, Pluggable Transports, and Proxies} 
Internet censors seek to block network resources through 
a variety of means, such as falsifying DNS responses, blocking IP addresses, 
filtering keywords, and detecting protocols by deep packet inspection.
Censors can block the Tor network by blocking the list of Tor relays, which 
are public. Blocking Tor becomes challenging when
the Tor network is augmented with \emph{bridges} and \emph{pluggable transports}.
Fig.~\ref{fig:topology} illustrates the interacting components.

\begin{figure}
\centering
\includegraphics{topology.pdf}
\caption{
The chain of components involved in connecting to a website over Tor.
Most users do not need a proxy;
similarly only those users who face a censor need a bridge.
In the diagram, ``Tor'' represents all three anonymizing hops through the Tor network.
We have shown the bridge as a separate component
because of the special role it plays.
When a bridge is used, it takes the place of the first Tor hop.
}
\label{fig:topology}
\end{figure}

Bridges are unlisted Tor relays that make it possible for a user to connect
to the Tor network even if a censor blocks all publicly listed Tor relays.
Pluggable transports are special protocols that run on bridges and obfuscate
Tor's network protocol to make it difficult to detect. 
Configuring a bridge requires providing one or more
``bridge lines,'' a specification of a bridge that
includes its IP address, transport type, and other metadata.
For ease of use, the interface has hard-coded options for 
the user to choose a group of bridges that use a particular
pluggable transport. For example, choosing  the hard-coded obfs3 option
configures a handful of bridges that use obfs3 pluggable transport.
Some censors block the IP addresses of the hard-coded bridges by looking
at the source code for those addresses (except flashproxy and meek).
If the built-in bridges do not work, a user can obtain bridge lines
through out-of-band channels, for instance by email~\cite{bridgedb}.
Fig.~\ref{fig:bridge-options} paraphrases the bridge configuration
options at the time of the study and lists the available pluggable transports.
%Some transports connect directly to a static IP address,
%obfuscating traffic to defeat on-the-wire identification;
%they rely on the secrecy of their IP addresses for their effectiveness.
%These include ``fte'' and ``fte-ipv6''~\cite{fte},
%which make Tor look like another protocol such as HTTP; and
%``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
%which encrypt Tor to look like random noise.
%Other transports work differently and do not depend on connecting to a static IP address:
%``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
%and the three ``meek''~\cite{fifield2015blocking} options route traffic
%through content delivery networks.

\begin{figure}
  \centering
    \includegraphics[width=0.5\textwidth]{bridge-options.png}
%\small
%\begin{itemize}
%\renewcommand{\labelitemi}{$\circ$}
%\item Connect with provided bridges\\
%Transport type:
%\begin{itemize}
%\item flashproxy
%\item fte
%\item fte-ipv6
%\item meek-amazon
%\item meek-azure
%\item meek-google
%\item obfs3 (recommended)
%\item obfs4
%\item scramblesuit
%\end{itemize}
%\item Enter custom bridges\qquad\fbox{Help}\\
%\end{itemize}
\caption{
Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
Users are not familiar with the options under ``Transport type'' denote various
built-in circumvention technologies (``pluggable transports'').
Under ``Enter custom bridges,'' there is a space to paste in
a bridge line, obtained out of band.
The ``Help'' button displays instructions on obtaining
bridge lines. 
}
\label{fig:bridge-options}
\end{figure}

In addition to Tor-specific components, a proxy may be necessary to connect 
outside the local network in certain managed environments, such as corporate or university networks.
Configuring a proxy requires providing the proxy protocol, IP address, port, and additional optional
fields. There is no assistance or automation with this process. The user must locate the 
proxy information and correctly input this information.

%Technically the Tor client, pluggable transport bridge, and proxy are all
%proxies. In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such
%as a SOCKS or HTTP proxy. An important distinction is that the local proxy lies within the 
%censor's control.

\subsection{Circumventing Censorship with Tor}
There are many valid configuration settings to connect to the Tor network.
For instance, a user who does not need a bridge or proxy 
can connect to Tor with a bridge and proxy, provided that they have been configured correctly. 
The minimum amount of configuration required, therefore, the set of valid configuration settings,
vary depending on the censorship environment. In the worst case, users must know or find out:\\

\begin{itemize}
	\item{Whether their Internet connection is censored} 
	\item{Whether the Tor network is censored by their ISP}
	\item{Which hard-coded bridges work in their country} 
	\item{If no hard-coded bridges work, how to get custom bridge information and connect to it} 
	\item{Whether a proxy is required to access the Internet}
	\item{If a proxy is required, and if so, the proxy settings}
\end{itemize}

Uncensored users and users in censorship environments that do not explicitly 
block Tor do not require a bridge or a proxy and can bypass these steps in the configuration process.
Users in censorship environments that explicitly block Tor but have not blocked the 
hard-coded bridges in the Tor Launcher source code are required to use a 
hard-coded bridge or custom bridge to connect to Tor. Users in a censorship environment that has explicitly 
blocked Tor relays and hard-coded bridges are required to configure a meek bridge (which 
routes traffic through content delivery networks and therefore resists blocking through collateral damage) or 
configure a custom bridge to connect to Tor.

\section{Evaluation Criteria and Goals}
\label{sec:goals}
Our user studies evaluated two versions of the Tor Launcher interface.
The first, which we have labeled OLD in our figures and tables,
is the current version being distributed with Tor Browser.
The second, NEW, is the prototype that we designed
in order to provide better usability. Below are the empirical and 
heuristic evaluation criteria we use to assess the interfaces.

Our empirical evaluation criteria for the Tor Browser configuration
interface are based on common metrics that measure ease of use: \\

\begin{enumerate}
    \item {\bfseries Success rate:} what percentage of users can successfully connect to Tor in a given condition. This measures how many users are able to configure their connections with the interface. 
    \item {\bfseries  Time to completion:} how long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for the connection to bootstrap. This measures how much time is required for a user to connect to the Tor network. 
    \item {\bfseries Active configuration time:} how much time a user spends actively configuring network components to connect to Tor, which only includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap. This measures how much of the time spent connecting to the Tor network was spent configuring versus waiting. 
\end{enumerate}

An ideal interface maximizes the amount of people that successfully connect to the Tor network, while minimizing the time it takes to connect to the Tor network. A trade-off may be required between the total amount of time it takes to connect to Tor and the amount of time users interact with the interface. For instance, a  process with a balanced amount of user input may be faster than a naive but completely automated process.

\section{Experimental Setup}
\label{sec:environments}
For our experiments, we use instrumented versions of Tor Browser~5.0.3, 
the most recent stable release at the time~\cite{torbrowser-503}.
Though there were new releases during the experiments,
we used the same version across all participants to not introduce
confounding factors.

For both user studies, we simulated three censorship environments,
which we refer to as E1, E2, and E3, which are in  the order of increasing severity.
We designed the environments to be representative
of what, in our estimation, are important real-world
cases of censorship. They are not intended to imitate
any particular country's censorship environment.\\

\begin{description}
\item [E1: Mild censorship.]
(Representative of countries such as France and Australia.)
The E1 environment only blocks some websites,
as if by DNS poisoning.
We blocked subdomains of torproject.org
and wikipedia.org.
(The participants' main goal in the experiment was to read a page on en.wikipedia.org.)
To succeed in this environment,
participants only had to click ``Connect'' on the first screen;
additional configuration was optional.

\item [E2: Intermediate censorship.]
(Representative of countries such as Tunisia.)
The E2 environment blocks websites as in E1 and
additionally blocks IP addresses of public Tor relays
and directory authorities, simulating a censor who knows
about circumvention and tries to stop it.
In this environment, simply clicking ``Connect'' does not work;
participants had to select a built-in bridge
(any type other than ``flashproxy'' would work).
A custom bridge would work but was not necessary.

\item [E3: Comprehensive censorship.]
(Representative of countries such as China and Syria.)
The E3 environment blocks websites and Tor relays like E1 and E2
and additionally blocks built-in default bridge IP addresses in the Tor Browser source code.
To succeed in this environment, participants had to select
one of the ``meek'' built-in bridges (no other type of hard-coded bridges would work)
or acquire their own custom bridge and enter it manually.
\end{description}

\smallskip

Table~\ref{tab:environments} summarizes our simulated censorship
environments. We used features of the Windows operating system 
to implement the above blocking behaviors.
To simulate website blocking, we added entries to the hosts file,
mapping domain names to the address 127.0.0.1.
We used Windows Firewall rules for IP address blocking.

\begin{table}
\centering
\begin{tabular}{r c c c}
& E1 & E2 & E3 \\
% \noalign{\hrule}
websites blocked & X & X & X \\
public relays blocked & & X & X \\
default bridges blocked & & & X \\
\end{tabular}
\caption{
Summary of our simulated censorship environments.
E1 only requires participants to click ``Connect'';
E2 requires selection of a built-in bridge;
and E3 requires selection of a specific type of built-in bridge,
or manual configuration of a custom bridge.
E2's blocking is a superset of E1's;
similarly E3's is a superset of E2's.
}
\label{tab:environments}
\end{table}

\section{Qualitative Analysis of the Existing Interface (Study 1)}
\label{sec:qualitative}

We ran a qualitative, exploratory user study to gain an 
understanding of how users interact with the configuration interface and
what common problems may be. We did this by observing participants using 
the interface to circumvent censorship and interviewing them about
their experience.  Our observations during this study guided us in
redesigning the interface and provided hypotheses to test in our quantitative study.

\subsection{Inspection}
We used a combination of usability inspection methods~\cite{nielsen1994usability}
to prepare for the user study. Two researchers conducted a pluralistic 
walkthrough and stepped through various censorship
scenarios, discussing which elements would be involved for that use case, and walking 
through the configuration process. After compiling all the possible paths through the 
interface, researchers performed feature inspection, listing sequences of features used 
to accomplish typical tasks and taking note of long sequences or cumbersome
steps. In addition, we performed a heuristic evaluation to mark
likely causes of confusion for users during our study.

\subsection{Recruitment}
Using established practices from the field of user experience research~\cite{howmanyusers},
we recruited 16 participants across the three censorship environments:
5~in E1, 5~in E2, and 6~in E3.
We pre-screened~\cite{screening} our participants for diversity of gender, age, technical expertise,
and self-reported familiarity with Tor in each simulated censorship environment for our summative
usability test~\cite{summative}.

We recruited our users from Craigslist, vaguely asking to evaluate a piece of software. 
The recruitment text can be found in Appendix~\ref{qualitative-recruitment}. The recruitment posting contained a 
SurveyGizmo online survey that collected their demographics, technical expertise, and familiarity with Tor.
The complete prescreening survey can be found in Appendix~\ref{qualitative-prescreening}.  
We selected participants in each censorship environment to have at least one person who has never heard of Tor, 
at least one person who has only heard of Tor, and exactly one person who has previously used Tor. We tried to evenly distribute any participants who had technical
expertise or used particular security tools throughout the censorship environments.

Of our 16 participants, 53.3\% were male. 
Ages ranged from 20 to~62 years
($\mu = 24.5$, $\sigma = 12.6$). 
93.3\% of our participants had at least
a college education.
4 had used Tor before;
5 had heard of Tor but not used it;
and the remaining 8 had never heard nor used it.

\subsection{Procedure}
The one-hour, single-participant procedure begun when a participant entered a small 
room with a single computer, which is equipped with Tor, Chrome, Firefox, Internet Explorer, and VLC.
Each participant is informed of the risks and purpose of the study.
A researcher informed the participant of the simulated censorship environment and
instruct them to visit sample blocked and unblocked websites
in a standard browser (Appendix~\ref{qualitative-script}). 
This shows participants what a blocked site looks like in a browser. 
Then, the participant was asked to complete a worksheet that gives information
on their censorship environment and instructed them
to visit one blocked website and one non-blocked website (Appendix~\ref{participant-worksheet}).
The worksheet informed the participant that the network is censored,
but did not give details of what services and websites are specifically blocked.
Participants were able to visit the unblocked website using any familiar browser,
but had to configure Tor Browser in order to visit the blocked website.

For the blocked website, we used the main page of Wikipedia,
and for the unblocked site we used the CNN homepage.
We chose these two sites because of their likely familiarity to web users;
our goal was to evaluate the user interface, not to test users with a browsing task.
After instructions, the researchers stepped out of the room.There was no interaction
between the participant and researcher for the rest of the session.
Researchers watched a live video of each participant's screen from another room
and saved the videos for review; the resulting videos and summaries
are available from our project page.
Participants had an average of 45 minutes to complete their worksheet.

After participants completed the browsing tasks or ran out of time,
we interviewed them about their experience and
took notes of the questions and answers.
We asked questions asking about their general experience, 
interface features they found confusing, and feedback for improvements (Appendix~\ref{interview-questions}). 
We followed up with specific questions prompted from watching their screen. 
This was to verify any hypotheses we had (e.g. ``they did not know what an ISP was'').
We paid each participant~\$30 for their time.

\subsection{Results} 
We discuss six common challenges our participants encountered during the configuration process.
Participant quotations come from live transcription during the post-experiment interview
and are not necessarily verbatim.\\

\begin{description}
\item {\bfseries Users did not understand what proxies, bridges, and pluggable transports were.}
Most participants, including those pre-screened for high technical ability and previous experience with Tor, were not familiar with the vocabulary.

\smallskip
\pquote{P2}{I don't know what any of those [list of bridges] means, or what that [proxy] means at all.}
\smallskip
\pquote{P3}{The vocabulary is really challenging, for someone not doing IT work.}
\smallskip

\item {\bfseries Users did not know if they should connect directly or configure a connection.}
Participants incorrectly determined that a blocked torproject.org website meant that Tor relays were censored, configuring bridges and proxies when they did not need to. Other participants tried a direct connection because they did not know what to do, but configuring their connection seemed hard.

\item {\bfseries Users did not know how to choose which bridge and pluggable transport to use.}
On the bridge configuration screen, participants were confused by the names of the bridge transports. The most common behavior was to configure with the recommended bridge option (obfs3). If the recommended one did not work, participants did not know how to choose another.

\smallskip
\pquote{P8}{I have no clue what's the difference between flashproxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?}
\smallskip
%\pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen. I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).}

\item {\bfseries Users did not know when they are wrong.}
Unfortunately, many mistakes did not result in error messages, but warnings that went unnoticed.
When participants did encounter an error message, they did not understand what errors meant (Fig.~\ref{fig:error}).

\item {\bfseries Users assumed they are wrong when they are right.}
The progress bar has a bug that causes it to update only when the level of progress increases.
If progress bar reaches a 90\% and fails, the next attempt have regressed to 0\% and remain there until the progress surpasses 90\%. Due to this, participants assumed that their subsequent attempts were wrong, even if they were right.

\smallskip
\pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}
\smallskip
\pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}
\smallskip

\item {\bfseries Users assume that proxy is required after a failed connection.}
All of our participants who failed to connect (5 of 16) failed for this reason. Many mistakenly assumed that they needed a proxy upon failure, because the interface redirects to the proxy screen (the last screen) after failure.

\smallskip
\pquote{P15}{I didn't know if this computer had any proxy information. I wasn't able to find it if it did.}
\end{description}

From interviewing our participants, we found that these challenges are the result of these underlying causes: \\

\begin{description}
\item {\bfseries Users do not know how to connect to Tor.} Participants did not know the difference between a direct connection and an indirect connection to the Tor network or the difference among bridges, pluggable transports, and proxies. Participants did not know how to configure these network components without explicit additional instructions. 
\item {\bfseries Feedback is too technical, missing, or misleading.} Participants did not know when they failed, since certain mistakes do not trigger error warnings or timeouts (i.e. a syntactically correct but invalid proxy). If participants did see an error message, they did not understand it. The progress bar bug also caused users to wrongly assume they were not making progress since it did not give feedback on subsequent attempts. 
\item {\bfseries Users do not understand censorship circumvention cues.} With enough technical background, there are  signals to what components are necessary and unnecessary. A connection to the Internet indicates that no proxy is required. A failed direct connection indicates a blocked Tor relay. A failed hard-coded bridge connection indicates a blocked bridge relay. However, the average user does not understand these signals.
\end{description}

The challenges users faced in the qualitative experiment and the respective underlying causes are used as feedback for redesigning the configuration interface.

\begin{figure}[t]
  \centering
    \includegraphics[width=0.5\textwidth]{error.png}
    \caption{An example of a technical error message which our participants did not understand.}
\label{fig:error}
\end{figure}

\section{Redesigning the Configuration Interface}
We make ten changes to the Tor launcher configuration interface to help users connect to Tor. Since users did not know how to connect to Tor, we added advice where our users have previously struggled. Specifically, the following three changes were made to give users more information in during configuration: \\

\label{redesign}

 \begin{figure*}[t]
	\centering
		\includegraphics[width=.8\textwidth]{bridge-screens.pdf} 
		\caption{In the OLD interface, users are asked, ``Does your Internet Service Provide (ISP) block or 
		otherwise censor connections to the Tor Network?'' (B1). A ``Yes'' determines that a bridge should 
		be configured and directs to the bridge configuration screen (B2). 
		The NEW interface gives users advice on configuring bridges
		while giving the option of not configuring a bridge, on one screen (B).} 
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=.8\textwidth]{proxy-screens.pdf} 
		\caption{In the OLD interface, users are asked, ``Does this computer need a local proxy to connect
		to the Internet?'' (P1). A ``Yes'' determines that a proxy should be configured and directs to the 
		proxy configuration screen (P2). The NEW interface checks the local machine's proxy settings,
		and informs the user whether a proxy is required, and if so, what those settings are (P).}
\end{figure*}

\begin{figure*}[t]
\centering
\includegraphics[width=.85\textwidth]{old-and-new-flows.png}
\caption{
Comparison of user flow in the OLD and NEW interfaces.
We collapsed the two bridge screens into one 
and also collapsed the two proxy screens into one.
We swapped the order of the bridge and proxy configuration
so it matches the order of network components (compare with Fig.~\ref{fig:topology}).
We added a summary screen as a last step before initiating a connection.\\
\textbf{F}: first screen;
\textbf{B/B1/B2}: bridge screens;
\textbf{P/P1/P2}: proxy screens;
\textbf{S}: summary screen;
\textbf{Pr}: progress bar.
}
\label{fig:flow}
\end{figure*}

\begin{enumerate}
\item Added instructions on what to try next on errors. When an error occurs, text advice on what to try next is shown to the user to help them recover from the error. The advice may be to try the connection again, to choose a different bridge, or to try a connection without a proxy. 
\item Added guidance on choosing between connect and configure. Before, the interface only informed users that the connect option worked some of the time, but did not specify why that was so. We labeled the configure option as a manual option  specifically for users in heavily censored environments.
\item Added explicit advice on choosing bridge transports. Users did not know which bridges to choose if they were in E3, which requires users to choose a meek or custom bridge. We added text that advises users to try a meek bridge if obfs3 does not work.
\end{enumerate}

Users found the feedback to be more confusing than helpful, since error messages were technical and progress bar was misleading. We make the following changes to make feedback insightful and reflective of system state:\\ 
\begin{enumerate}
\setcounter{enumi}{3}
\item Progress bar feedback is accurate.  We fixed the bug that caused the progress bar to not update on subsequent attempts. What users now see on the progress bar reflects the reality of the progress. 
\item Made the interface text less technical. We made the text more task-centric by focusing on instructing users through the configuration process. Since users generally did not understand the technical concepts sufficiently to influence their decisions, we think giving direct guidance is a better option. 
\item Added system status visibility. Before beginning any connection attempt, a summary screen displays the current bridge and proxy settings. The same information is shown on the progress screen while the connection is in progress. We switched the continuous progress bar to a discrete checkpoint-based progress indicator that shows the network components involved in connecting to the Tor network.
\end{enumerate}

Our users had little technical background. We made the following changes to make the interface more compatible for the average user: \\

\begin{enumerate}
\setcounter{enumi}{6}
\item Eliminated technical questions.  We removed the gating questions that determined whether a bridge and proxy should be configured, which were highly technical and challenging for users to answer. This are two fewer screens in the revised interface. 
\item Added auto-detection of proxies. In principle, the interface can guess whether a proxy is needed by scanning the operating system configuration. This purely local detection does not carry any risks nor reveal to network eavesdroppers that the user is using Tor. (We simulated the auto-detection by hard-coding the fact that a proxy was not required.)
\item Switched ordering to configure proxies first. To build users' mental models, network components are now configured in a topologically sequential order, resembling Fig.~\ref{fig:topology} and the new progress screen. Previously, proxies were put after bridge configuration because only a small fraction of users require proxies. With auto-detection, configuring a proxy before a bridge burdens users less than before.
\end{enumerate}

These changes result in a redesigned interface which we refer to as NEW. Note that the new interface preserves all the functionality of the old interface and still allows users to have control over their own network traffic.

\section{Quantitative Analyses of the Interfaces (Study 2)}
\label{sec:quantitative}
Having identified problems with the existing interface
and made changes to ameliorate them,
we quantify the existing problems
and the impact of our changes with a study involving a larger number of users.
We split participants by simulated censorship environments,
and between old and new interfaces.

\subsection{Setup}
We ran our experiment at Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of 
California, Berkeley. Xlab has 36 Windows~7 laptops, separated by cubicle walls. 
Though Tor Browser runs on other operating systems,
testing was only done on Windows, as a byproduct of using Xlab.

We augmented the interfaces with instrumentation 
to log every meaningful interaction
(button presses, menu selections, screen changes).
We wrote scripts to automatically set up the simulated censorship environment, install necessary software, 
start the video recording, and save the logs and videos.
We recorded the participants' computer screens
throughout the experiment to capture non-interface activity such as 
web searching and inspection of system networking settings.

\subsection{Recruitment}
We recruited 124 participants, about 20 for each
condition. We recruited half of our users from Craigslist, and half of our participants from 
the Xlab participant pool. Although Xlab participants are not limited to UC Berkeley students and staff,
a majority of the participants are from campus. For this reason, we chose to recruit 
half of our participants from Craigslist to ensure a diverse set of participants. 
The recruitment text vaguely suggests testing a piece of software, and does not require
that users provide information in advance (Appendix~\ref{quantitative-recruitment}). 
Out of our 124 participants, 59 were recruited from the Xlab pool and the other 65 were
recruited from Craigslist. Ages ranged from 18 to~68 years
($\mu = 28.9$, $\sigma = 12$). 56.8\% were male and 
84.8\% of our participants had at least a college education.

\subsection{Procedure}
The one-hour, multi-participant procedure began when all participants sat at their
respective computers in Xlab. Each computer was equipped with an instrumented old or new version
of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording).
Each computer was assigned one of the six conditions in the beginning of the study. Participants
were assigned to a simulated censorship environment combination at random.

A researcher informed the participants that they are in a
simulated censorship environment, instructed them to visit a sample blocked website on a 
non-Tor browser of their choice to illustrate the situation, and asked them to 
complete a worksheet that asks to visit one blocked website (Appendix~\ref{quantitative-script}). 
To mirror the qualitative study, we chose Wikipedia's featured article of the day 
as the blocked website to visit on their worksheet.

After instructions, researchers maintained minimal interactions with the participants, 
only answering logistical questions.
The participants did not know the details of their censorship environment,
only that they are being censored. Participants had 40 minutes to configure Tor Browser to 
circumvent the simulated censorship and visit the blocked website.

After users completed the browsing tasks, they took a short exit survey (Appendix~\ref{quantitative-exit-survey})
that collected their demographics. All users were instructed to sit until the end of the experiment,
regardless of when they had completed their task. After the 40 minutes, 
participants were officially informed that their time was up, and were given their payment of 
\$30 for their time.

\subsection{Results} 
The possible interface version and environment combinations resulted in 6 experimental conditions. We recruited 124 participants to aim for about 20 participants per condition. We filtered participants who downloaded their own version of Tor Browser or did not sign the consent form, resulting in 114 participants. Table~\ref{table:participant-summary} summarizes the rate of success, time to success, and active time for our participants' by condition.

\begin{table}
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r r}
	& \multicolumn{2}{r}{success rate} & \multicolumn{1}{r}{median time} &\multicolumn{1}{r}{median}\\
	& \multicolumn{2}{r}{after 40 minutes} & \multicolumn{1}{r}{to success} & \multicolumn{1}{r} {active time} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 & 0:06 \\
	E1-OLD & 19/19 & 100\% & 1:01 & 0:24 \\
	E2-NEW & 18/18 & 100\% & 3:22 & 0:40 \\
	E2-OLD & 16/19 & 84\% & 5:00 & 2:04 \\
	E3-NEW & 13/19 & 68\% & 12:38 & 1:56 \\ 
	E3-OLD & 10/20 & 50\% & 40:08 & 9:06 \\
	\end{tabular}
\caption{
A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were assigned the maximum time of 40:08.
}
\label{table:participant-summary}
\end{table}

\subsubsection{Rate of Success} 
49 of 56 (88\%) participants with the new interface successfully connected to Tor, while 45 of 58 (78\%) participants with the old interface did. Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference. Appendix~\ref{stat-tests} details the methodology for the statistical tests used in this paper.

%\begin{figure}[t]
%\centering
%\includegraphics[width=.5\textwidth]{warning.png}
%\caption{
%A screenshot of the interface with the ``Copy Tor Log to Clipboard'' button, 
%which appears silently and does not interrupt the progress bar. 
%This warning was generated by entering in syntactically correct but invalid proxy settings,
%a mistake that prevents users from ever connecting to the Tor network. 
%Users are never directly notified of this error through an error message or a timeout message.
%Our participants made this error during our experiments, along with others that they were not notified about. 
%}
%\label{fig:warning}
%\end{figure}

>>>>

\begin{tabular}{r c c c c c c}
& \rotatebox{90}{E1-NEW} & \rotatebox{90}{E1-OLD} & \rotatebox{90}{E2-NEW} & \rotatebox{90}{E2-OLD} & \rotatebox{90}{E3-NEW} & \rotatebox{90}{E3-OLD} \\
no bridge, no proxy & 17 & 13 &  &  &  &  \\
obfs3, no proxy & 2 & 6 & 18 & 16 &  &  \\
meek-amazon, no proxy &  &  &  &  & 7 & 4 \\
meek-google, no proxy &  &  &  &  & 5 & 4 \\
meek-azure, no proxy &  &  &  &  & 1 & 1 \\
no bridge, 3rd-party proxy &  &  &  &  &  & 1 \\
DNF (did not finish) &  &  &  & 3 & 7 & 9 \\
\end{tabular}
